Random Forest

### 2021-11-19 code/analysis_code/04-Mods.P2.LASSO.rmd
Update Models

---
title: "Best Tree"
author: "MYC"
date: "11/14/2021"
output: html_document
---

@@

2.5. Hyper parameter tuning
```{r}

```

2.6. Model evaluation
     - Regression
       - minimize
         - MSE
         - RMSE
         - Deviance
         - MAE
         - RMSLE
       - maximize
         - R^2
     - classification
       - minimize
         - Misclassifcation
         - Mean per class e rror
         - MSE
         - Cross-entropy -- log loss/deviance
         - Gini index
       - maximize
         - Accuracy
         - Precision
         - Sensitivity / recall
         - Specificity
         - AUC

```{r}

```

Tree model
```{r}
tree_model <-  decision_tree() %>% 
  set_args( cost_complexity = tune(), tree_depth = tune(), min_n = tune()) %>% 
  set_engine("rpart") %>% 
  set_mode("regression")      
```
Workflow
```{r}
#set workflow
tree_wf <- workflow() %>%
  add_model(tree_model) %>%
  add_recipe(fit_recipe)
```
Tree Model
```{r}
#tuning grid
tree_grid <- dials::grid_regular(cost_complexity(), tree_depth(), min_n(), levels = 5)
#tune the model
tree_tune_res <- tree_wf %>% 
  tune::tune_grid(
    resamples = cv_data,
    grid = tree_grid,
    metrics = yardstick::metric_set(rmse) 
  )
```

```{r}
#see a plot of performance for different tuning parameters
tree_tune_res %>% autoplot()
```

```{r}
# get the tuned model that performs best 
best_tree <- tree_tune_res %>%  select_best(metric = "rmse")
# finalize workflow with best model
best_tree_wf <- tree_wf %>% finalize_workflow(best_tree)
# fitting best performing model
best_tree_fit <- best_tree_wf %>% 
                 fit(data = train_data)
#predicting outcomes for final model
tree_pred <- predict(best_tree_fit, train_data)
```

```{r}
rpart.plot(extract_fit_parsnip(best_tree_fit)$fit)
```

```{r}
#predicted versus observed
plot(tree_pred$.pred,train_data$Ct, xlim =c(0,100), ylim=c(0,100))
abline(a=0,b=1, col = 'red') #45 degree line, along which the results should fall

```

```{r}
#residuals
plot(tree_pred$.pred-train_data$Ct)
abline(a=0,b=0, col = 'red') #straight line, along which the results should fall
```

```{r}
tree_perfomance <- tree_tune_res %>% show_best(n = 5)
print(tree_perfomance)
```

>>>>

---
title: "LASSO"
author: "MYC"
date: "11/14/2021"
output: html_document
---

@@

# LASSO Linear model

## Set up
```{r}
#model
lasso_model <- linear_reg() %>%
  set_mode("regression") %>%           
  set_engine("glmnet") %>%
  set_args(penalty = tune(), mixture = 1) #mixture = 1 means we use the LASSO model

#workflow
lasso_wf <- workflow() %>%
  add_model(lasso_model) %>% 
  add_recipe(fit_recipe)
```

## Tuning
```{r}
#tuning grid
lasso_reg_grid <- tibble(penalty = 10^seq(-3, 0, length.out = 30))

#tune model
lasso_tune_res <- lasso_wf %>% 
  tune_grid(resamples = cv_data,
            grid = lasso_reg_grid,
            control = control_grid(save_pred = TRUE),
            metrics = metric_set(rmse)
            )
```

## Evaluation

```{r}
#see a plot of performance for different tuning parameters
lasso_tune_res %>% autoplot()
```

#
```{r}
# get the tuned model that performs best 
best_lasso <- lasso_tune_res %>%  select_best(metric = "rmse")

# finalize workflow with best model
best_lasso_wf <- lasso_wf %>% finalize_workflow(best_lasso)

# fitting best performing model
best_lasso_fit <- best_lasso_wf %>% 
  fit(data = train_data)
lasso_pred <- predict(best_lasso_fit, train_data)
```

```{r}
x <- best_lasso_fit$fit$fit$fit
plot(x, "lambda")
```
Variables that are part of the best-fit LASSO model, i.e. those that have a non-zero coefficient.
```{r}
tidy(extract_fit_parsnip(best_lasso_fit)) %>% filter(estimate != 0)
```

Plotting observed/predicted and residuals.
```{r}
#predicted versus observed
plot(lasso_pred$.pred,train_data$Ct, xlim =c(15,50), ylim=c(15,50))
abline(a=0,b=1, col = 'red') #45 degree line, along which the results should fall
```
```{r}
#residuals
plot(lasso_pred$.pred-train_data$Ct)
abline(a=0,b=0, col = 'red') #straight line, along which the results should fall
```
Looks decent, the points are along the red lines in the plot

## Model Performance
```{r}
lasso_perfomance <- lasso_tune_res %>% show_best(n = 5)
print(lasso_perfomance)
```

### 2021-11-19 code/analysis_code/04-Mods.P2.RandomForest.rmd
Update Models

---
title: "LASSO"
author: "MYC"
date: "11/14/2021"
output: html_document
---

@@

# LASSO Linear model

## Set up
```{r}
#model
lasso_model <- linear_reg() %>%
  set_mode("regression") %>%           
  set_engine("glmnet") %>%
  set_args(penalty = tune(), mixture = 1) #mixture = 1 means we use the LASSO model

#workflow
lasso_wf <- workflow() %>%
  add_model(lasso_model) %>% 
  add_recipe(fit_recipe)
```

## Tuning
```{r}
#tuning grid
lasso_reg_grid <- tibble(penalty = 10^seq(-3, 0, length.out = 30))

#tune model
lasso_tune_res <- lasso_wf %>% 
  tune_grid(resamples = cv_data,
            grid = lasso_reg_grid,
            control = control_grid(save_pred = TRUE),
            metrics = metric_set(rmse)
            )
```

## Evaluation

```{r}
#see a plot of performance for different tuning parameters
lasso_tune_res %>% autoplot()
```

#
```{r}
# get the tuned model that performs best 
best_lasso <- lasso_tune_res %>%  select_best(metric = "rmse")

# finalize workflow with best model
best_lasso_wf <- lasso_wf %>% finalize_workflow(best_lasso)

# fitting best performing model
best_lasso_fit <- best_lasso_wf %>% 
  fit(data = train_data)
lasso_pred <- predict(best_lasso_fit, train_data)
```

```{r}
x <- best_lasso_fit$fit$fit$fit
plot(x, "lambda")
```
Variables that are part of the best-fit LASSO model, i.e. those that have a non-zero coefficient.
```{r}
tidy(extract_fit_parsnip(best_lasso_fit)) %>% filter(estimate != 0)
```

Plotting observed/predicted and residuals.
```{r}
#predicted versus observed
plot(lasso_pred$.pred,train_data$Ct, xlim =c(15,50), ylim=c(15,50))
abline(a=0,b=1, col = 'red') #45 degree line, along which the results should fall
```
```{r}
#residuals
plot(lasso_pred$.pred-train_data$Ct)
abline(a=0,b=0, col = 'red') #straight line, along which the results should fall
```
Looks decent, the points are along the red lines in the plot

## Model Performance
```{r}
lasso_perfomance <- lasso_tune_res %>% show_best(n = 5)
print(lasso_perfomance)
```

>>>>

---
title: "Random Forest"
author: "MYC"
date: "11/14/2021"
output: html_document
---

@@

```{r}
rf_model <- rand_forest() %>%
  set_args(mtry = tune(),     
    trees = tune(),
    min_n = tune()
  ) %>%
  # select the engine/package that underlies the model
  set_engine("ranger",
             num.threads = 18, #for some reason for RF, we need to set this in the engine too
             importance = "permutation") %>%
  # choose either the continuous regression or binary classification mode
  set_mode("regression")   
```

```{r}
#workflow
rf_wf <- workflow() %>%
  add_model(rf_model) %>% 
  add_recipe(fit_recipe)
```

```{r}
#tuning grid
rf_grid  <- expand.grid(mtry = c(3, 4, 5, 6), min_n = c(40,50,60), trees = c(500,1000)  )

# tune the model, optimizing RMSE
rf_tune_res <- rf_wf %>%
  tune_grid(
            resamples = cv_data, #CV object
            grid = rf_grid, # grid of values to try
            metrics = metric_set(rmse) 
  )
```

```{r}
#see a plot of performance for different tuning parameters
rf_tune_res %>% autoplot()
```
```{r}
# get the tuned model that performs best 
best_rf <- rf_tune_res %>%  select_best(metric = "rmse")

# finalize workflow with best model
best_rf_wf <- rf_wf %>% finalize_workflow(best_rf)

# fitting best performing model
best_rf_fit <- best_rf_wf %>% 
  fit(data = train_data)
rf_pred <- predict(best_rf_fit, train_data)
```

```{r}
#pull out the fit object
x <- best_rf_fit$fit$fit$fit
#plot variable importance
vip::vip(x, num_features = 20)
```
Meaning that the point of Tool B is the most important/predicitive variable for Ct outcome

```{r}
#predicted versus observed
plot(rf_pred$.pred,train_data$Ct, xlim =c(10,50), ylim=c(10,50))
abline(a=0,b=1, col = 'red') #45 degree line, along which the results should fall
```
```{r}
#residuals
plot(rf_pred$.pred-train_data$Ct)
abline(a=0,b=0, col = 'red') #straight line, along which the results should fall
```
```{r}
rf_perfomance <- rf_tune_res %>% show_best(n = 5)
print(rf_perfomance)
```
